SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/metaty.tex
checkpoint

\subsection{Share Type Checking with Annotations}

>>>>

\section{$\metaprot$ Type Checking}

Now we develop a compositional type system for $\metaprot$ based on 
$\minicat$ typing and the automated Hoare logic developed in
Section \ref{section-metalang}. We focus on share types for confidentiality
which is more complex and general than our integrity type system.
An algorithmic approach to the latter was developed previously for
$\metaprot$ \cite{skalka-near-esop25}, and also the core element
of the system-- BDOZ/SPDZ-style MAC checking-- can be treated as
algebraic correctness conditions enforceable by Hoare triples
as we show in Section \ref{section-examples}.

\subsection{Share Type Checking with Annotations}
\label{section-metaty}
